---
title: "Assigment - kNN - dataset HCV"
author: "Dang Nguyen" 
#Author review: Kien Huynh
date: "28/02/2022"
output:
   html_notebook:
    toc: true
    toc_depth: 2
---


```{r}
library(tidyverse)
library(googlesheets4)
library(class)
library(caret)
library(magrittr)
library(plotly)
```

---
## A. Business understanding
The data set contains laboratory values of blood donors, Hepatitis C patients and their demographic values.

## B. Data Understanding
```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/assignments/master/datasets/KNN-hcvdat0.csv"
rawDF <- read_csv(url, )
str(rawDF)
```

## C. Data Preparation
### 1. Data cleaning
```{r}
cleanDF <- na.omit(rawDF[-1])
head(cleanDF)
```

### 2. Setting labels to category types (defined as either "Donor" or "Hepatitis")
```{r}
cleanDF$Category <- factor(cleanDF$Category)
levels(cleanDF$Category) <- c("Donor", "Donor", "Hepatitis", "Hepatitis", "Hepatitis")
levels(cleanDF$Category)
table(cleanDF$Category)
```
### 3. Visualizing an inspection between ALB and ALP
```{r}
p1 <- ggplot(cleanDF) +
  geom_point(aes(ALB, ALP, colour = Category))
p1
```


## D. Normalize numeric features
### 1. Setting a function 
```{r}
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x))) 
}
```
### 2. Testing the function 
```{r}
testSet1 <- c(1:5)
testSet2 <- c(1:5) * 10

cat("testSet1:", testSet1, "\n")
cat("Normalized testSet1:", normalize(testSet1), "\n")

cat("testSet2:", testSet2, "\n")
cat("Normalized testSet2:", normalize(testSet2), "\n")
```


```{r}
nCols <- dim(cleanDF)[2]
cleanDFnorm <- sapply(4:nCols,
                    function(x) {
  normalize(cleanDF[, x])
}) %>% as.data.frame()

head(cleanDFnorm)
```

## E.Preparing train and test datasets
```{r}
s <- sample(c(1:dim(cleanDF)[1]), 469)

#Splitting training and test data sets
trainDFfeat <- cleanDFnorm[s,  ]
testDFfeat <- cleanDFnorm[-s,  ]

#Creating training and test data sets with labels
trainDFlabels <- cleanDF[s, 1]
testDFlabels <- cleanDF[-s, 1]
```


## F. Modeling and Evaluation
```{r}
cleanDFpred <- knn(train = as.matrix(trainDFfeat), test = as.matrix(testDFfeat), cl = as.matrix(trainDFlabels), k = 7)
head(cleanDFpred)
confusionMatrix(cleanDFpred, testDFlabels[[1]], positive = NULL, dnn = c("Prediction", "True"))
dim(cleanDFpred)
dim(testDFlabels)
```

## G. Evaluation and Deployment
k = 7 seems to provide the best accuracy in this example. Yet I do not know why after trying a few times.

reviewer adds suggestions for improving the model..
